Fractional anisotropy as an optimal tracer of cosmic voids

### 2014-08-12 cosmic_voids.tex
Description of the T-web scheme

With the above parameters the mass of each particle in the simulation is 
$m_{\rm p}=1.4\times 10^{8}$\hMsun. Throughout this paper we shall use a
catalogue of halos identified through the Bound Density Maximum algorithm
\citep{Klypin99}. These halos have been selected to have an overdensity of
200 times the critical density in addition to be mutually excluded of the
virial radius of other halos. Mass, comoving position and peculiar 
velocity of each halo at $z=0$ were obtained through the public available 
Multidark database \footnote{\url{http://www.multidark.org/MultiDark/}} 
\citep{Riebe11}. For estimating the density and velocity fields we use a 
\textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then, 
through a finite-difference scheme, the tidal and shear tensors are 
computed. Finally the eigenvalues and eigenvectors of each tensor are 
obtained for each cell of the grid. Neglecting substructures presented 
below Megaparsec scales and taking into account our focus in voids, which 
are a prominent characteristic of the Megaparsec Universe, we apply a 
Gaussian softening of one cell to all our fields.

%*************************************************************************
\section{Algorithms to quantify the cosmic web}
\label{sec:algorithms_cosmic_web}
%*************************************************************************

@@

The first algorithm  we use to identify the cosmic web is based upon the
diagonalization of the tidal tensor, defined as the Hessian of a 
normalized gravitational potential

@@

%.........................................................................
%Poisson
\begin{equation}
\nabla^2\phi = \delta,
\end{equation}
%.........................................................................
where $\bar{\rho}$ is the average density in the Universe, $G$ is the 
gravitational constant and $\delta$ is the dimensionless matter 
overdensity.

>>>>

With the above parameters the mass of each particle in the simulation is 
$m_{\rm p}=1.4\times 10^{8}$\hMsun. Throughout this paper we shall use a
catalogue of halos identified through the Bound Density Maximum algorithm
\citep{Klypin99}. These halos have been selected to have an overdensity of
200 times the critical density in addition to be mutually excluded of the
virial radius of other halos. Mass, comoving position and peculiar 
velocity of each halo at $z=0$ were obtained through the public available 
Multidark database \footnote{\url{http://www.multidark.org/MultiDark/}} 
\citep{Riebe11}. For estimating the density and velocity fields we use a 
\textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then 
through finite-differences and FFT methods the tidal and shear tensors 
are computed. Finally the eigenvalues and eigenvectors of each tensor are
obtained for each cell of the grid. Neglecting substructures presented 
below Megaparsec scales and taking into account our focus in voids, which 
are a prominent characteristic of the Megaparsec Universe, we apply a 
Gaussian softening of one cell to all fields.

%*************************************************************************
\section{Algorithms to quantify the Cosmic Web}
\label{sec:algorithms_cosmic_web}
%*************************************************************************

@@

This scheme was initially proposed by \citet{Hahn07} as a novel 
alternative for classifying the Cosmic Web based upon the tidal tensor, 
that is somehow more fundamental than the density field as it also allows 
to quantify the orbital dynamics of the matter field. This approach is 
reached by a second-order expansion of the equations of motion around 
local minima of the gravitational potential and then extended to any 
position. The second-order term corresponds to the tidal tensor, which is 
defined as the Hessian of the normalized gravitational potential

@@

%.........................................................................
%Poisson
\begin{equation}
\nabla^2\phi = \delta,
\end{equation}
%.........................................................................
with $\bar{\rho}$ the average density in the Universe, $G$ the 
gravitational constant and $\delta$ the dimensionless matter overdensity.

Since the tidal tensor can be represented in any cell by a real and 
symmetric $3\times 3$ matrix, it is ensured the possibility to diagonalize 
it and obtain three real eigenvalues $\lambda_{1} > \lambda_{2}>\lambda_3$.
This set of eigenvalues can be used as indicators of the local orbital 
stability in each proper direction, which in turn can be translated into 
a classification scheme of the Cosmic Web. A counting of the number of 
positive (stable) or negative (unstable) eigenvalues allows to catalogue
a single cell into one of the next four types of environment: voids (3 
negatives eigenvalues), sheets (2), filaments (1) and knots (0). A 
significant improvement to this scheme was introduced by \citet{Forero09}
by means of a relaxation of the stability criterion. The relative strength 
of each eigenvalue is no longer defined by the sign, but instead by a
threshold value $\lambda_{th}$ which can be tuned in such a way that the
visual impression of the web-like matter distribution is reproduced.
